Downscaling coarse observations to predict continuous species spatio-temporal distribution

### 2022-05-06 Version_M2_plusieurszones/pres/RESSTE_2022/RESSTE_2022.Rmd
RESSTE

---
title: "Infering species distribution from aggregated spatial data"
subtitle : "Going from coarse landings data to fine scale species distribution"
author : "Baptiste Alglave, Marie-Pierre Etienne, Kasper Kristensen, Youen Vermard,  Mathieu Woillez, Etienne Rivot"

@@

@@

\textbf{Punctual observation model} ($Y_i$):

\tiny \vspace{\baselineskip} \footnotesize

\textbf{Declaration model} ($D_j=\sum_{i \in \mathcal{P}_j}{Y_{i}}$):

\begin{align*}
P(D_j = 0) & = \prod_{i\in \mathcal{P}_j} P(Y_{i} = 0)
                      = \exp{ \left \lbrace- \sum_{i\in \mathcal{P}_j} e^{\xi}. S(x_{i})\right \rbrace} = \pi_j.
\end{align*}

$$\operatorname{P}\left(D_j=d_{j} \vert d_j > 0 \right) =  \operatorname{L}\left(d_{j},\mu_j = E(D_j|d_j>0),\sigma_j^2 = ln(\frac{Var(D_j|d_j>0)}{E(D_j|d_j>0)^2} + 1) \right)$$

>>>>

---
title: "Downscaling coarse observations to predict continuous species spatio-temporal distribution"
subtitle : "Going from coarse landings data to fine scale fish distribution"
author : "Baptiste Alglave, Marie-Pierre Etienne, Kasper Kristensen, Youen Vermard, Mathieu Woillez, Etienne Rivot"

@@

\textbf{Punctual observation model} ($Y_i$)

\normalsize \vspace{\baselineskip} \vspace{\baselineskip}

\textcolor{BaptisteLightGreen}{\textbf{Declaration model}} ($D_j=\sum_{i \in \mathcal{P}_j}{Y_{i}}$)

\begin{align*}
P(D_j = 0) & = \prod_{i\in \mathcal{P}_j} P(Y_{i} = 0)
                      = \exp{ \left \lbrace- \sum_{i\in \mathcal{P}_j} e^{\xi}. S(x_{i})\right \rbrace} = \pi_j
\end{align*}

$$\operatorname{P}\left(D_j=d_{j} \vert d_j > 0 \right) = \quad \textbf{?}$$

### Specifying $\operatorname{P}\left(D_j=d_{j} \vert d_j > 0 \right)$

\normalsize

\textbf{Compute the moments}

\vspace{\baselineskip}
\vspace{\baselineskip}

\normalsize

\textbf{Consider $D_j$ is Lognormal too}

$$
\begin{aligned}
&\operatorname{P}\left(D_j=d_{j} \vert d_j > 0 \right) = \\ \\ & \quad \quad \operatorname{L}\left(d_{j},\mu_j = E(D_j|d_j>0),\sigma_j^2 = ln(\frac{Var(D_j|d_j>0)}{E(D_j|d_j>0)^2} + 1) \right)
\end{aligned}
$$

@@
